A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
small changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@954 43ef1190-90fd-4dd7-a769-d0121f02b80e

This results in an NQuads file per host, which is then loaded into a
SPARQL Endpoint\todo{which} for analysis by using the statistics
system R\todo{ref}.

@@

First, we investigated whether certain servers provided better support
for caching than others. To do this, we formulated SPARQL queries to
examine the \httph{Server} headers of successful responses, with
optional clauses matching the standard-compliant computed freshness
time (which is the ideal) as well as whether the response had other
promising features that could assist caching, such as \httph{ETag}s,
modification time, certain predicates, etc.

@@

In Figure\todo{figure with over freshness}, there is a barplot where
the freshness lifetime is grouped in bins, where the first bin are the
cases where caching is explicitly prohibited. The next bins are for
lifetimes, where the values are grouped if they are on the order of
seconds, minutes, hours, etc, i.e. the second bin counts the lifetimes
in the interval \[1,59\] seconds, etc. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.

>>>>

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL Endpoint for analysis by using the statistics
system R\todo{ref}.

@@

First, we investigated whether certain servers provided better support
for caching than others. To do this, we formulated SPARQL queries to
examine the \httph{Server} headers of successful responses, with
optional clauses matching the standard-compliant computed freshness
time (which is the ideal) as well as whether the response had other
promising features that could assist caching, modification time,
certain predicates, etc.

@@

In Figure\todo{figure with over freshness}, there is a barplot where
the freshness lifetime is grouped in bins, where the first bin are the
cases where caching is explicitly prohibited. The next bins are for
lifetimes, where the values are grouped if they are on the order of
seconds, minutes, hours, etc, i.e. the second bin counts the lifetimes
in the interval [1,59] seconds, etc. We see that in these
categories, the most common is to prohibit caching. Nevertheless, many
also declare a standards compliant freshness lifetime in minutes to
days.
